Unshuffling Permutations

### 2015-07-01 article.tex
Quelques notations

% Définir :
% - notation $[n]$
% - ensemble $S$
% - standardisation $\STD$
% - notation $\pi_{|P}$ et $\pi_{|\bar P}$
% - notation $\widetitle{\pi} (miroir)
% - notation $\bar \pi$ (complémentaire)
% - notation $\bar ^{-1}$ (inverse)

>>>>

We denote by $S_n$ the set of permutations of size $n$ and by $S$ the
set of all permutations. If $\pi$ is a permutation, we denote by $|\pi|$
its size. If $P$ is a subset of $[|\pi|]$, $\pi_{|P}$ is the subword of
$\pi$ consisting in the letters of $\pi$ at the positions specified by
the elements of $P$. Besides, we denote by $\widetilde{\pi}$ (resp.
$\bar \pi$, $\pi^{-1}$) the mirror image (resp. complementary, inverse)
of $\pi$. If $u$ is a word of integers without multiple occurrences of a
same letter, $\STD(u)$ denotes the unique permutation of same size as
$u$ such that for all $i, j \in [|u|]$, $u_i < u_j$ if and only if
$\STD(u)_i < \STD(u)_j$.
\medskip
